On a Alvenicity of solar wind discontinuities

### 2024-08-20 article.qmd
update articles

::: {.column-page}
::: {#fig-examples layout-nrow="1" }

Three examples of solar wind discontinuities observed by Parker Solar Probe (PSP), Wind and ARTEMIS spacecraft.

:::
:::

@@

::: {.column-page}
::: {#fig-profiles layout-nrow="1" }

![](figures/profiles_sym.svg)

![](figures/J_profiles_sym.svg)

(a). Magnetic field, ion density, and ion bulk velocity for $n_1 = n_2, u_1 = -u_2$ and $δ_1=1, c_1=1/\sqrt{2}, B_0 = 2$. (b). Current density profiles for the same case.
:::
:::

@@

We normalize the plasma velocity by asympotic Alfvén velocity $v_{A}(∞) = B_0 / \sqrt{\mu_0 m_i n}$, and the profiles are plotted below @fig-profilesC. It could be seen that for $n_1(∞) = 0.5$, we have zero bulk velocity change across the current sheet in the asymptotic limit. And the change of bulk velocity across the current sheet increases with $n_1(∞)$ decreasing to zero @fig-uxnorm. The normalized plasma velocity $U_y$ in the aympotic limit decreases with $n_1(∞)$ decreasing to zero @fig-uynorm.

::: {.column-page}
::: {#fig-profilesC layout-nrow="1" }

![Magnetic field, ion density, and ion bulk velocity for two ion species with same bulk velocity but different densities.](figures/profiles_ratio=0.5.svg){#fig-profiles_ratio}

@@

:::
:::

@@

::: {.column-page}
::: {#fig-uProfilesNorm layout-nrow="1" }
![Plasma velocity $U_x$ profiles normalized by $v_{A,x}$ for different $n_1(∞)$.](figures/UxNormBx.svg){#fig-uxNormBx}

![Plasma velocity $U_y$ profiles normalized by $v_{A,y}$ for different $n_1(∞)$.](figures/UyNormBy.svg){#fig-uyNormBy}
:::
:::

@@

::: {.column-page}
::: {#fig-vRatios layout-nrow="1" }
![](figures/vRatios.svg){#fig-vRatiosEx1}

@@

Asymptotic velocity for each species, bulk velocity and normalized one by Alfvén velocity for the case of $\lambda_{z,2} = - 1$ (a) and $\lambda_{z,2} = - 1/2$ (b).
:::
:::

>>>>

::: {#fig-examples}

![](figures/fig_examples.svg)

Three examples of solar wind discontinuities observed by Parker Solar Probe (PSP), ARTEMIS and Wind spacecraft with sub-Alfvenic flow velocity.

:::

@@

::: {#fig-profiles layout-ncol="2" }

![](figures/profiles_sym.svg){#fig-profilesEx1}

![](figures/J_profiles_sym.svg){#fig-jprofilesEx1}

(a). Magnetic field, ion density, and ion bulk velocity for $n_1 = n_2, u_1 = -u_2$ and $δ_1=1, c_1=1, B_0 = 2$. (b). Current density profiles for the same case.

:::

@@

::: {#fig-profilesEx2 layout-ncol="2" }

![](figures/profiles_n1Inf=0.6.svg)

![](figures/J_profiles_n1Inf=0.6.svg)

Same as @fig-profiles, but for two ion species with same bulk velocity but different densities $n_1(∞) = 0.6$ and $B_y(z=\infty) = 1/2 B_0$.

:::

We normalize the plasma velocity by asympotic Alfvén velocity $v_{A}(∞) = B_0 / \sqrt{\mu_0 m_i n}$, and the profiles are plotted in @fig-profilesEx2 for the case of $n_1(∞) = 0.6$. 
@fig-uxnorm It could be seen that for $n_1(∞) = 0.5$, we have zero bulk velocity change across the current sheet in the asymptotic limit. And the change of bulk velocity across the current sheet increases with $n_1(∞)$ decreasing to zero. The normalized plasma velocity $U_y$ in the aympotic limit decreases with $n_1(∞)$ decreasing to zero @fig-uynorm.

::: {#fig-profilesC layout-nrow="1" }

@@

:::

@@

<!-- ::: {.column-page} -->
::: {#fig-uProfilesNorm layout-nrow="1" }
![Plasma velocity $U_x$ profiles normalized by $v_{A,x}$ for different $n_1(∞)$.](figures/UxNormBx.svg){#fig-uxNormBx}

![Plasma velocity $U_y$ profiles normalized by $v_{A,y}$ for different $n_1(∞)$.](figures/UyNormBy.svg){#fig-uyNormBy}
:::
<!-- ::: -->

@@

<!-- ::: {.column-page} -->
::: {#fig-vRatios layout-nrow="1" }
![](figures/vRatios.svg){#fig-vRatiosEx1}

@@

Asymptotic velocity for each species, bulk velocity and normalized one by Alfvén velocity for the case of $\lambda_{z,2} = - 1$ (a) and $\lambda_{z,2} = - 1/2$ (b).
:::
<!-- ::: -->
